%!TEX encoding = UTF8
%!TEX root =cv-llt.tex

\begin{rubric}{Skills}
\noentry{2014 -- 2015}
\entry*[Research\hfill]
	BSc Mathematics Project: Simulated an 81-neuron Hopfield model and produced a novel investigation into the pattern recognition capabilities. \vspace{0.2cm} \newline
    Published a journal paper on hysteresis in continuous and discrete neuron models with adaptive feedback synapses. 
\entry*[Strengths\hfill]
	Exceptional logical thinking and problem-solving skills, developed and utilised through my BSc in Mathematics. Experienced in technical writing and producing clear, well-structured reports, demonstrated in both my award-winning final-year mathematics project and my highly graded MSc Data Science courseworks.
\entry*[Teamwork\hfill]
        Collaborated in a group of five on a second-year project involving research, presentation, and report writing on the logistic map, demonstrating effective teamwork and coordination. Also developed strong teamwork skills while coordinating closely with colleagues and kitchen staff during my time working at the pub.
\entry*[Communication\hfill]
        Strong interpersonal and communication skills developed through customer-facing work in a busy pub environment and collaborative projects with peers during lab sessions throughout my studies.
\entry*[Learning\hfill]
Highly motivated and quick to grasp new concepts, with a strong enthusiasm for continuous learning and tackling complex challenges. Proven ability to acquire new technical skills and adapt to unfamiliar tools or frameworks, particularly in data science and programming contexts.
\entry*[AI\hfill]
Excellent understanding of Artificial Intelligence and Large Language Models, including how they function and how to apply them effectively. Experienced in utilising AI tools to automate workflows, enhance productivity, and solve practical problems in data analysis and programming contexts.
\entry*[Other]
	Three years of driving experience, clean license. Languages: English (native), Spanish (basic).
    
\subrubric{Technical Proficiencies}

\entry*[Python\hfill]
	Experienced with modules such as \texttt{Pandas} and \texttt{TensorFlow}, working in \texttt{Jupyter Notebook} and \texttt{Google Colab}, and connecting to databases using \texttt{sqlite3}.
\entry*[R\hfill]
	Strong understanding; proficient with packages such as \texttt{ggplot2} and \texttt{tidyverse} in \texttt{RStudio}.
\entry*[MATLAB\hfill]
	Used during undergraduate studies to solve mathematical problems, particularly for my final year project.
\entry*[\LaTeX\hfill]
Extensive experience using \LaTeX\ via Overleaf for academic writing and technical documents. Used for two published academic papers, CV, and numerous coursework reports during my MSc, demonstrating proficiency in professional formatting, typesetting, and document structuring.
\entry*[Other\hfill]
        Excel, PowerPoint, Tableau, GitHub, and Orange Data Mining.
\end{rubric}
